### 2019-11-06 paper_lap/05apparatus.tex
updates

The following corollary follows immediately from the previous result.
\begin{corollary}
Let $A$ be the $N\times N$ matrix obtained by discretizing the interior Dirichlet problem and $S_\epsilon$ be the collection of functions defined in Definition \ref{def:seps}. Then for all functions $f,g \in S_\epsilon$
\begin{align}
\left| \langle {\bf g}, (A^T)^{-1}{\bf f} \rangle - \int_0^L g(t)\,\sigma(t)\,{\rm d}t \right| < \epsilon \|f\|\, \|g\|,
\end{align}
where ${\bf f},{\bf g}$ are the discretizations of $f$ and $g$ scaled by the square roots of the discretization weights, and $\sigma$ is the solution to the exterior Neumann problem with boundary data $f$.
\end{corollary}

@@

\begin{remark1}
We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than a panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie. the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
\end{remark1}
\begin{remark1}
Similarly, if the point $\by \in \mathbb{R}^2 \setminus \Omega$ at which the solution to the Neumann boundary value problem is to be calculated lies close to a smooth panel then the density $\sigma$ near that point can be interpolated to a finer set of quadrature points and the value of $u(\by)$ can once again be obtained to precision $\epsilon.$ We note, however, that in general the density in the vicinity of a corner cannot be interpolated accurately. This follows from the fact that the interpolation scheme constructed is only guaranteed to interpolate the powers arising in the Dirichlet problem accurately near the corner. The Neumann problem expansions contain negative powers which are not contained in this set and hence are not interpolated accurately.
\end{remark1}

\subsection{Weak corner re-solving}
In this section we address the problem highlighted in the previous one; namely, the accurate evaluation of the solution to the exterior Neumann problem in the vicinity of a corner. Our approach is based on the observation that the contribution from the density on the boundary outside of a sufficiently small neighborhood of the corner is smooth when evaluated in the vicinity of the corner. This allows us to convert the problem of evaluating the potential near the corner (given the approximation to the density obtained using the adjoint approach described in the previous section) into a purely local one. In particular, we rediscretize only a small neighborhood of the corner which in turn allows us to evaluate the potential arbitrarily close to the corner to within a small factor of machine precision.

In the following we assume that we are given a discretization of the interior Dirichlet boundary integral equation (\ref{}) with nodes $x_1,\dots,x_N$ and corresponding weights $w_1,\dots,w_N.$ In particular, we assume that the discretization nodes are obtained by subdividing the boundary into panels. Those panels which contain a vertex are discretized using a custom discretization scheme (see Section \ref{}) while the remaining panels are discretized using a standard smooth quadrature rule (such as Gauss-Legendre or Chebyshev nodes). In the following we assume that an $M$-point Gauss-Legendre quadrature rule is used. Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{}) by $A.$ Let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem. Finally, let $\underline{\sigma}$ be the approximation to the density (scaled by the square roots of the weights) obtained by solving the linear system
\begin{align}\label{eqn:adj_linalg}
A^T \underline{\sigma} = \underline{f}.
\end{align}
For notational convenience we let $\gamma:[-\delta,L-\delta] \to \partial \Omega$ be a counterclockwise arclength parametrization of $\partial \Omega$ such that  $\gamma(0)$ corresponds to a vertex and $\gamma[-\delta,\delta]$ corresponds to a corner panel.

For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$). Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ (see \cite{} for a detailed description of this process and quantitative estimates on the accuracy of the result).\\

{\color{red}add remark about ratio of size of panel to distance from the corner}\\

@@

In light of this we consider the following integral equation
\begin{align}\label{eqn:resolve_neum0}
-\sigma(s) + \int_{-\delta}^\delta k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -\delta \le s \le \delta.
\end{align}
We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of (\ref{}) restricted to the interval $[-\delta,\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
\begin{align}\label{eqn:resolve_diri0}
-\sigma(s) + \int_{-\delta}^\delta k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -\delta \le s \le \delta.
\end{align}
which is a Dirichlet boundary integral equation for a wedge with a piecewise analytic right-hand side. In particular, we can discretize the operator using the method summarized in the previous section. Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{} (see \cite{} for a detailed description of the method). Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights. Let $A_0$ be the discretization of the interior Dirichlet problem operator (ie. the operator acting on $\sigma$ on the left-hand side of (\ref{eqn:resolve_diri0})). We note that due to the scale invariance of Laplace's equation for polygonal domains the portion of $A_0$ corresponding to the self-interaction of $L_0$ is a submatrix of the original matrix $A.$ All other blocks can be generated using the discretization nodes as quadrature nodes.

@@

This can be represated to obtain an interpolable approximation to the density on $L_0 = [-\delta/2,\delta/2].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $L_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain. In particular, if we define
\begin{align}
h_1(s) = \sum_{x_i \in I_0,J_0} k(s,x_i) \sigma_0^{(i)} \sqrt{w_i}
\end{align}
then $\sigma$ restricted to the interval $L_0$ satisfies
\begin{align}\label{eqn:resolve_neum1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}
The corresponding adjoint equation is given by 
\begin{align}\label{eqn:resolve_diri1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}

>>>>

The following corollary follows immediately from the previous result.
\begin{corollary}
Let $A$ be the $N\times N$ matrix obtained by discretizing the interior Dirichlet problem and $S_\epsilon$ be the collection of functions given by Definition \ref{def:seps}. Then for all functions $f,g \in S_\epsilon$
\begin{align}
\left| \langle {\bf g}, (A^T)^{-1}{\bf f} \rangle - \int_0^L g(t)\,\sigma(t)\,{\rm d}t \right| < \epsilon \|f\|\, \|g\|,
\end{align}
where ${\bf f},{\bf g}$ are the discretizations of $f$ and $g$ scaled by the square roots of the discretization weights, and $\sigma$ is the solution to the exterior Neumann problem with boundary data $f$.
\end{corollary}

@@

\begin{remark1}
We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than a panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie. the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
\end{remark1}
\begin{remark1}
Similarly, if the point $\by \in \mathbb{R}^2 \setminus \Omega$ at which the solution to the Neumann boundary value problem is to be calculated lies close to a smooth panel then the density $\sigma$ near that point can be interpolated to a finer set of quadrature points and the value of $u(\by)$ can once again be obtained to precision $\epsilon.$ We note, however, that in general the density in the vicinity of a corner cannot be interpolated accurately. This follows from the fact that the interpolation scheme constructed is only guaranteed to interpolate the powers arising in the Dirichlet problem accurately near the corner. The collection of singular powers arising in Neumann problems contain negative powers which are not contained in this set and hence are not interpolated accurately.
\end{remark1}

\subsection{Weak corner re-solving}
In this section we address the problem highlighted in the previous one; namely, the accurate evaluation of the solution to the exterior Neumann problem in the vicinity of a corner. Our approach is based on the observation that the potential generated by the density on the boundary outside of a sufficiently small neighborhood of the corner is smooth when evaluated in the vicinity of the corner. This allows us to convert the problem of evaluating the potential near the corner (given the approximation to the density obtained using the adjoint approach described in the previous section) into a purely local one. In particular, we re-discretize only a small neighborhood of the corner which in turn allows us to evaluate the potential arbitrarily close to the corner to within a small factor of machine precision.

In the following we assume that we are given a discretization of the interior Dirichlet boundary integral equation (\ref{bie_intd}) with nodes $x_1,\dots,x_N$ and corresponding weights $w_1,\dots,w_N.$ In particular, we assume that the discretization nodes are obtained by subdividing the boundary into panels. Those panels which contain a vertex are discretized using a custom discretization scheme (see Section \ref{sec:disc_dir}) while the remaining panels are discretized using a standard smooth quadrature rule (such as Gauss-Legendre or Chebyshev nodes). In the following we assume that an $M$-point Gauss-Legendre quadrature rule is used. Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $A.$ Let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem. Finally, let $\underline{\sigma}$ be the approximation to the density (scaled by the square roots of the weights) obtained by solving the linear system
\begin{align}\label{eqn:adj_linalg}
A^T \underline{\sigma} = \underline{f}.
\end{align}
For notational convenience we let $\gamma:[-\delta,L-\delta] \to \partial \Omega$ be a counterclockwise arclength parametrization of $\partial \Omega$ such that  $\gamma(0)$ corresponds to a vertex and $\gamma[-\delta,\delta]$ corresponds to a corner panel.

For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$). Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ (see \cite{} for a detailed description of this process and quantitative estimates on the accuracy of the result). Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner.

@@

In light of this we consider the following integral equation
\begin{align}\label{eqn:resolve_neum0}
-\sigma(s) + \int_{-\delta}^\delta k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -\delta \le s \le \delta.
\end{align}
We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of the original boundary integral equation (\ref{bie_extn}) restricted to the interval $[-\delta,\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
\begin{align}\label{eqn:resolve_diri0}
-\sigma(s) + \int_{-\delta}^\delta k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -\delta \le s \le \delta.
\end{align}
which is a Dirichlet boundary integral equation for a wedge with a piecewise analytic right-hand side. In particular, we can discretize the operator using the method summarized in the previous section. Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{} for a detailed description of the method). Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights. Let $A_0$ be the discretization of the interior Dirichlet problem operator (ie. the operator acting on $\sigma$ on the left-hand side of (\ref{eqn:resolve_diri0})). We note that due to the scale invariance of Laplace's equation for polygonal domains the portion of $A_0$ corresponding to the self-interaction of $L_0$ is a submatrix of the original matrix $A.$ All other blocks can be generated using the discretization nodes as quadrature nodes.

@@

\begin{remark}
Though the above method produces a viable method for reducing the problem, as written the reduction is non-local --- in order to compute the right-hand side for the sub-problem one must evaluate contributions from the rest of the domain.
\end{remark}

The following theorem shows that the right-hand side $\underline{f}_0$ can be computed only using local data (i.e. values of the weak solution in the vicinity of the corner).
\begin{theorem}
Let $\underline{f}_0$ be the discretization of the right-hand side of (\ref{eqn:resolve_diri0}). 
\end{theorem}

This can be represented to obtain an interpolable approximation to the density on $L_0 = [-\delta/2,\delta/2].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $L_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain. In particular, if we define
\begin{align}
h_1(s) = \sum_{x_i \in I_0,J_0} k(s,x_i) \sigma_0^{(i)} \sqrt{w_i}
\end{align}
then $\sigma$ restricted to the interval $L_0$ satisfies
\begin{align}\label{eqn:resolve_neum1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}
The corresponding adjoint equation is given by 
\begin{align}\label{eqn:resolve_diri1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}
